Unshuffling Permutations

### 2016-02-10 new-article.tex
Modif LATIN16
LATIN 2016

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_2)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one arc between $\nu_1$ and $\nu_2$ in $\vv{\mathcal{M}}$
    (regardless of the orientation).
    Suppose now, aiming at a contradiction, that there exists
    exactly one arc between $\nu_1$ and $\nu_2$ in $\vv{\mathcal{M}}$.
    According to Corollary~\ref{corollary:reverse oriented matching} there is no
    loss of generality in assuming that this is a
    $(\nu_1, \nu'_1)$-arc, say $(a, a')$.
    Furtheremore, according to Lemma~\ref{lemma:for nu_1 and nu_2},
    there is no $(\nu_1, \nu_1)$-arc in $\vv{\mathcal{M}}$.
    Now, since $\nu_1$ is increasing and there exists
    exactly one $(\nu_1, \nu_2)$ in $\vv{\mathcal{M}}$,
    we conclude that
    $\vv{\mathcal{M}}$ contains $N_1-1$ pairwise crossing
    $(\nu_1, \nu'_1)$-arcs
    (this follows from the fact that $\vv{\mathcal{M}}$ does not contain \CrossingLR
    nor \CrossingRL).
    But $|\nu_1| = |\nu'_1| = N_1$ and $\vv{\mathcal{M}}$ is perfect,
    and hence there exists a position, say $y$, in $\nu'_1$ that is
    not involved in a $(\nu_1, \nu'_1)$-arc in $\vv{\mathcal{M}}$.
    We rule out this configuration by considering two cases:
    \begin{itemize}
      \item Position $y$ is involved in a $(\nu_2, \nu'_1)$-arc,
      say $(y', y)$.
      Then, we have $\mu(a) > \mu(y')$ (since $\nu_1$ is above $\nu_2$)
      and $\mu(a') < \mu(y)$ (since $\nu_2$ is below $\nu'_1$),
      which contradicts Property~$\mathbf{P_2}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 1}.
      \item
      Position $y$ is involved in a $(\nu'_1, \nu_2)$-edge,
      say $(y', y)$.
      According to Lemma~\ref{lemma:value inclusion of arcs},
      $(a, a')$ and $(y, y')$ must be crossing
      (\emph{i.e.}, $y < a'$).
      But it follows that $\vv{\mathcal{M}}$ contain \CrossingLR
      which contradicts Property~$\mathbf{P_1}$.
      \item
      $(y, y'')$ in an arc of $\vv{\mathcal{M}}$ for some
      $y'' > 2N_1 + N_2$.
      But $\nu'_1$ is above any other gadget, and hence
      applying Lemma~\ref{lemma:value inclusion of arcs} to
      arcs
      $(a, a')$ and $(y, y'')$ yields a contrdiction.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 2}.
    \end{itemize}
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:(nu_1, nu'_1)-edge}
    There is at least one $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:(nu_1, nu'_1)-edge}]
    Suppose, aiming at a contradiction, that there is no
    $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then it follows that there exists an edge $(x, x')$ in $\mathcal{M}$,
    $1 \leq x \leq N_1$, that is neither a
    $(\nu_1, \nu_1)$-edge (since $N_1$ is odd)
    nor a $(\nu_1, \nu_2)$-edge (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_1, \nu'_1)$ (by our contradiction hypothesis).
    (In other words, $x \leq N_1$ and $x' > 2N_1 + N_2$.)
    Therefore, since $\mathcal{M}$ is containment-free,
    there is neither a $(\nu_2, \nu_2)$-edge nor a $(\nu'_1, \nu'_1)$-edge
    in $\mathcal{M}$.
    Then it follows that every position $y$ of $\nu'_1$
    (\emph{i.e.}, $N_1+N_2 < y \leq 2N_1+N_2$)
    is involved in an edge $(y, y'$ of $\mathcal{M}$ with $y' \geq 2N_1+N_2$
    (otherwise $\mathcal{M}$ would not be containment-free).
    But $|\nu'_1| = N_1 = 2(2N_2 + 2n_3 + 2N_4 + 2n + 2k + 4) + 1
    > 2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4$, and hence at least one
    position in $\nu'_1$ can not be involved in an edge in $\mathcal{M}$.
    Then it follows that $\mathcal{M}$ is not a perfect matching,
    which contradicts our hypothesis about $\mathcal{M}$.
    \qed
  \end{proof}

>>>>

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_2)-edge}]
    First, according to Lemma~\ref{lemma:at most one edge monotone},
    there exists at most one arc between $\nu_1$ and $\nu_2$ in $\vv{\mathcal{M}}$
    (regardless of the orientation).
    Suppose now, aiming at a contradiction, that there exists
    exactly one arc between $\nu_1$ and $\nu_2$ in $\vv{\mathcal{M}}$.
    According to Corollary~\ref{corollary:reverse oriented matching}, there is no
    loss of generality in assuming that this is a
    $(\nu_1, \nu_2)$-arc and denote it by $(a, a')$.
    Furtheremore, according to Lemma~\ref{lemma:for nu_1 and nu_2},
    there is no $(\nu_1, \nu_1)$-arc in $\vv{\mathcal{M}}$.
    Now, since $\nu_1$ is increasing and there exists
    exactly one $(\nu_1, \nu_2)$ in $\vv{\mathcal{M}}$,
    we conclude that
    $\vv{\mathcal{M}}$ contains $N_1-1$ pairwise crossing
    $(\nu_1, \nu'_1)$-arcs
    (this follows from the fact that $\vv{\mathcal{M}}$ does not contain \CrossingLR
    nor \CrossingRL).
    But $|\nu_1| = |\nu'_1| = N_1$ and $\vv{\mathcal{M}}$ is perfect,
    and hence there exists a position, say $y$, in $\nu'_1$ that is
    not involved in a $(\nu_1, \nu'_1)$-arc in $\vv{\mathcal{M}}$.
    We rule out this configuration by considering two cases:
    \begin{itemize}
      \item Position $y$ is involved in a $(\nu_2, \nu'_1)$-arc,
      say $(y', y)$.
      Then, we have $\mu(a) > \mu(y')$ (since $\nu_1$ is above $\nu_2$)
      and $\mu(a') < \mu(y)$ (since $\nu_2$ is below $\nu'_1$),
      which contradicts Property~$\mathbf{P_2}$.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 1}.
      \item
      Position $y$ is involved in a $(\nu'_1, \nu_2)$-edge,
      say $(y', y)$.
      According to Lemma~\ref{lemma:value inclusion of arcs},
      $(a, a')$ and $(y, y')$ must be crossing
      (\emph{i.e.}, $y < a'$).
      But it follows that $\vv{\mathcal{M}}$ contains \CrossingLR
      which contradicts Property~$\mathbf{P_1}$.
      \item
      $(y, y'')$ in an arc of $\vv{\mathcal{M}}$ for some
      $y'' > 2N_1 + N_2$.
      But $\nu'_1$ is above any other gadget, and hence
      applying Lemma~\ref{lemma:value inclusion of arcs} to
      arcs
      $(a, a')$ and $(y, y'')$ yields a contrdiction.
      See Fig.~\ref{subfig:no (nu_1, nu_2)-edge - 2}.
    \end{itemize}
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:(nu_1, nu'_1)-edge}
    There is at least one $(\nu_1, \nu'_1)$-arc in $\vv{\mathcal{M}}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:(nu_1, nu'_1)-edge}]
    Suppose, aiming at a contradiction, that there is no arc between
    $\nu_1$ and $\nu'_1$ in $\vv{\mathcal{M}}$.
    Then it follows that there exists an arc $(x, x')$ or
    $(x', x)$ in $\vv{\mathcal{M}}$,
    $1 \leq x \leq N_1$, that is neither a
    $(\nu_1, \nu_1)$-arc (since $N_1$ is odd)
    nor a $(\nu_1, \nu_2)$-arc or a $(\nu_2, \nu_1)$-arc
    (Claim~\ref{claim:no (nu_1, nu_2)-edge})
    nor a $(\nu_1, \nu'_1)$-arc or $(\nu_1, \nu'_1)$-arc
    (by our contradiction hypothesis).
    (In other words, $x \leq N_1$ and $x' > 2N_1 + N_2$.)
    Therefore, since $\mathcal{M}$ avoids
    \InclusionLL,~\InclusionLR,~\InclusionRL and \InclusionRR
    (part of Property~$\mathbf{P_1}$),
    there is neither a $(\nu_2, \nu_2)$-arc nor a
    $(\nu'_1, \nu'_1)$-arc in $\mathcal{M}$.
    Then it follows that every position $y$ of $\nu'_1$
    (\emph{i.e.}, $N_1+N_2 < y \leq 2N_1+N_2$)
    is involved in an arc $(y, y')$ or $(y', y')$ in
    $\vv{\mathcal{M}}$ with $y' \geq 2N_1+N_2$
    (otherwise $\mathcal{M}$ would contain
    \InclusionLL,~\InclusionLR,~\InclusionRL or \InclusionRR).
    But $|\nu'_1| = N_1 = 2(2N_2 + 2n_3 + 2N_4 + 2n + 2k + 4) + 1
    > 2N_2 + 2N_3 + 2N_4 + 2n + 2k + 4$, and hence at least one
    position in $\nu'_1$ can not be involved in an arc in $\vv{\mathcal{M}}$.
    Then it follows that $\vv{\mathcal{M}}$ is not a perfect matching,
    which contradicts our hypothesis about $\vv{\mathcal{M}}$.

    Combining tha aboce contradiction with
    Corollary~\ref{corollary:reverse oriented matching}, we may assume that
    $\vv{\mathcal{M}}$ contain at least one $(\nu_1, \nu'_1)$-arc
    (and hence no $(\nu'_1, \nu_1)$-arc).
    \qed
  \end{proof}
